### 2021-10-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
does no->does not

\replaced[comment={Abbreviation defined [4,1]}]{Supercritical carbon dioxide (sCO$_2$).}{Supercritical CO$_2$} Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}. The literature shows that the recompression cycle can reach efficiencies of 50\% in some scenarios (with turbine inlet temperatures in the 650-700 $^{\circ}$C range) \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures. Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar award for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated \replaced[comment={Abbreviations defined [4,1]}]{concentrating solar power (CSP) receiver, thermal energy storage (TES),.}{CSP receiver, TES,} and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. \replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does no incoporate thermal energy storage for meeting peak demand}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods. 
A CSP has an array of mirrors concentrating solar rays towards a \replaced[comment={Furthering explanation of the CSP [3,1]}]{tower receiver, transferring the energy into a solar salt, and storing the solar salt in tanks. CSP systems require direct sunlight to operate at full power therefore causing variability based on weather conditions and time of day.}{receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.} Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a \replaced[comment={Abbreviation defined [4,1]}]{lead-cooled fast reactor (LFR).}{LFR} is capable of transferring heat to thermal storage for later dispatch. An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C. Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles has been performed at Sandia National Laboratories \cite{wright_2011} and in Korea \cite{cha_2016}, with at least two commercial companies (Echogen, Net Power) having progressed to building pilot cycles  \cite{held_2015,fetvedt_2016}.

>>>>

\replaced[comment={Abbreviation defined [4,1]}]{Supercritical carbon dioxide (sCO$_2$).}{Supercritical CO$_2$} Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}. The literature shows that the recompression cycle can reach efficiencies of 50\% in some scenarios (with turbine inlet temperatures in the 650-700 $^{\circ}$C range) \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures. Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar award for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated \replaced[comment={Abbreviations defined [4,1]}]{concentrating solar power (CSP) receiver, thermal energy storage (TES),.}{CSP receiver, TES,} and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. \replaced[comment={Drawbacks of CSP and LFR technology elaborated on [2,2]}]{These drawbacks include CSP dependency on weather conditions and time of day, while the LFR in isolation does not incoporate thermal energy storage for meeting peak demand}{} Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods. 
A CSP has an array of mirrors concentrating solar rays towards a \replaced[comment={Furthering explanation of the CSP [3,1]}]{tower receiver, transferring the energy into a solar salt, and storing the solar salt in tanks. CSP systems require direct sunlight to operate at full power therefore causing variability based on weather conditions and time of day.}{receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day.} Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a \replaced[comment={Abbreviation defined [4,1]}]{lead-cooled fast reactor (LFR).}{LFR} is capable of transferring heat to thermal storage for later dispatch. An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C. Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles has been performed at Sandia National Laboratories \cite{wright_2011} and in Korea \cite{cha_2016}, with at least two commercial companies (Echogen, Net Power) having progressed to building pilot cycles  \cite{held_2015,fetvedt_2016}.
